My title

### 2022-02-06 outputs/paper/paper.Rmd
upadted

  The statistical programming language used to work with the data in this paper is R (@citeR) along with packages like tidyverse [@citytidyverse], knitr [@citeknitr]. The "COVID-19 Cases in Toronto" dataset was obtained from Open Data Toronto which houses a broad number of datasets. This data set was published by Toronto Public Health and for this paper, this dataset was officially imported from the opendatatoronto package in R.

>>>>

  The statistical programming language used to work with the data in this paper is R (@citeR) along with packages like tidyverse @citytidyverse, knitr @citeknitr. The "COVID-19 Cases in Toronto" dataset was obtained from Open Data Toronto which houses a broad number of datasets. This data set was published by Toronto Public Health and for this paper, this dataset was officially imported from the opendatatoronto package in R.
